---
title: "Using the fitmodel package"
author: "Mathurin Dorel"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the fitmodel package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Loading the library:
```{r}
library(fitmodel)
```

# Creation of the model

Create the model using the data and the network layout as previous knowledge, both provided as file names

```{r, eval=T}
setwd("../inst/extdata/")
model = createModel("network.tab", "HCT116_MIDAS.csv", "basal.dat", inits=10, init_distribution=T,
                    method="randomlhs");
```

Evaluate how the simulation compares to the data

```{r}
accuracyPlot(model)
plotModelPrediction(model, "all", "all")
```

```{r}
simulateModel(model, "all", "all")
```

## Figures

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.
Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
